Case based Arabic Morphological Analysis with Compositional Non-deterministic Automata

### 2010-06-25 trunk/tex/sarf.tex
added related work

Many morphological analyzers exist~\cite{Sughaiyer:04}. 
Some use specialized part of speech tag sets~\cite{Khoja:01,Darwish:02}.

Buckwalter: used lexicon, added proper nouns, word based, recursive affixes

@@

Beeseley: many compiled FSAs compared to compositions of three FSAs

@@

\subsection{Recursive Affixes}
% smaller FSM
% retain POS info

>>>>

The survey work in~\cite{Sughaiyer:04} discusses and compares
several morphological analyzers. 
Analyzers such as~\cite{Khoja:01,Darwish:02} 
target specific specific applications in the morphological 
analyzer itself or use a specific set of part of speech tags
as their reference.
Sarf differs in that it is a general and rich morphological 
analyzer that reports all possible solutions. 
It is case-based in the sense that a controller that drives
the morphological analyzers prunes these decisions. 
Up to our knowledge, Sarf is the only morphological analyzer
that addresses the ``run-on'' words problem.

Sarf builds upon the lexicon of Buckwalter\shortcite{Buckwalter:02}.
It differs than Buckwalter where it defines a shorter list of affixes
and a longer list of affix compatibility rules to allow recursive 
affixes so that we can have prefix-prefix an suffix-suffix 
concatenations.
This allows Sarf to better maintain and propagate 
the part of speech information
tags associated with each prefix while these need to be highly 
redundant with Buckwalter and that may lead to consistency issues. 
Sarf keeps the possible analyses alive as a sequence corresponding
to the text. Buckwalter produces a set of solutions for each token 
and the several analysis threads of the whole text need to be 
generated as a product of the token solutions.

Sarf is similar to Beeseley~\shortcite{Beeseley:01} in that it uses
finiste-state automata (FSA). 
Beeseley reports that the number of the automata generated by a compiler
from Xerox rules is not controlled and also reports a difficulty to 
compose the FSAs into a single FSA framework. 
Sarf solves the problem with a non-deterministic composition of three
FSAs that are the prefix, stem, and suffix FSAs. 
With Sarf it is easy to control the FSAs with a user custom case 
controller, while with Beeseley the effort requires recompiling the
Xerox rules.

@@

@@

Sarf extends the lexicon of Buckwalter~\shotcite{Buckwalter:02} with 
proper names and location names extracted from different online 
sources~\footnote{\hyperref{http://alasmaa.net/}{http://alasmaa.net/ }, 
    \hyperref{http://ar.wikipedia.org/}{http://ar.wikipedia.org/}}
as well as books 
\subsection{Recursive Affixes}
% smaller FSM
% retain POS info
